Moral Foundations of U.S. Political News Organizations

### 2019-03-25 pilot_manuscript.Rmd
adding more runs

>>>>

```{r Rush_shut, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)
library(lubridate)

url = "https://www.rushlimbaugh.com/?s=government%20shutdown&is_v=1"

#loop over the results and go through them
##18 pages
for (i in 1:47){

#pull only the right dates
rows = rownames(temp2[ (temp2$`5` == 2018 | temp2$`5` == 2019) & #must be 2018/19 and  
                         (
                           (temp2$`6` == "12" & as.numeric(temp2$`7`)>8 & temp2$`5` == 2018) | #after dec 12
                             (temp2$`6`== "01" & temp2$`5` == 2019) | #all of jan
                             (temp2$`6` == "02" & as.numeric(temp2$`7`)<8 & temp2$`5` == 2019)
                         ), #before feb 8
                       ])
urlslist3 = urlslist[as.numeric(rows)]

write.csv(RUSHDF, "RUSH_gs.csv", row.names = F)
